\documentclass[12pt,a4paper]{article}
\pdfoutput=1
\hoffset=-2cm 
\textwidth=17.5cm
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}  
\usepackage{braket}
%\usepackage{subcaption}

\usepackage[affil-it]{authblk}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}


\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.0}

%%%%%%%%%%%%%%%%%%%%%%%
\newcommand {\blue} {\color{blue}}
\newcommand {\cyan} {\color{cyan}}
\newcommand {\red} {\color{red}}
\newcommand {\magenta} {\color{Plum}}
\definecolor{NewYellow}{cmyk}{0.2,0.2,1,0.2}
\newcommand {\yellow} {\color{NewYellow}}
\definecolor{NewGreen}{rgb}{0,0.4,0}
\newcommand {\green} {\color{NewGreen}}
\newcommand{\rem}[1]{{\blue  #1}}
\newcommand{\comment}[1]{{\blue  #1}}
\newcommand{\erase}[1]{{\red     #1}}
\newcommand{\MET}{\textbf{\textit{E}$_{\rm T}^{\rm miss}$}}
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{subfigure}
%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\giac}[2]{{\blue #1 #2}}
\newcommand{\del}[1]{{\cyan #1}}

\begin{document}


\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.0}

\title{Anatomy of the Inert Two Higgs Doublet Model in the light of the LHC and non-LHC Dark Matter Searches}

\author[1,2]{Alexander Belyaev}
\author[3]{Giacomo Cacciapaglia}
\author[4]{Igor P. Ivanov}
\author[2,5]{Felipe Rojas}
\author[1,2]{Marc Thomas}

\affil[1]{Rutherford Appleton Laboratory, Didcot, United Kingdom}
\affil[2]{University of Southampton, Southampton, United Kingdom}
\affil[5]{Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso, Chile}
\affil[3]{Univ Lyon, Universit\'e Lyon 1, CNRS/IN2P3, IPNL, F-69622, Villeurbanne, France }
\affil[4]{CFTP, Instituto Superior T\'ecnico, Universidade de Lisboa, Lisbon, Portugal}

%\date{\today}
\maketitle
\vspace{0.8cm}
\begin{abstract}
The inert Two Higgs Doublet Model (i2HDM) is a theoretically well-motivated  example  of a
minimal consistent Dark Matter (DM)  model  which provides mono-jet, mono-$Z$, mono-Higgs and
Vector-Boson-Fusion+$\MET{}$ signatures at the LHC, complemented by signals in direct and
indirect DM search experiments. In this paper we have performed a detailed analysis of the  
constraints in the full 5D  parameter space of the i2HDM, coming from perturbativity, unitarity, electroweak
precision data, Higgs data from the LHC, DM relic density, direct/indirect DM detection and LHC
mono-jet analysis, as well as  implications of experimental LHC studies on disappearing charged
tracks relevant to high DM mass region. We demonstrate the complementarity of the above
constraints and present projections for future LHC data and direct DM detection
experiments to probe further i2HDM parameter space. The model is implemented into the CalcHEP and
micrOMEGAs packages, which are publicly available at the HEPMDB database, and is ready for a further
exploration in the context of the LHC, relic density and DM direct detection.


\end{abstract}

\newpage
\tableofcontents
\newpage


\input{1-Intro}
\input{2-Parameter-Space}
\input{3-numerical-scan}
\input{4-Collider-Pheno}
\input{5-Conclusions}

\section*{Acknowledgements}

AB thanks Tania Robens and Alexander Pukhov for useful discussions.
AB and MT acknowledge partial support from the STFC grant number  ST/L000296/1
and the NExT Institute, FAPESP grant 2011/11973-4 for funding their visit to ICTP-SAIFR as well as SOTON-FAPESP collaboration grant.
AB thanks the Royal Society Leverhulme Trust Senior Research Fellowship LT140094.
MT acknowledges support from an STFC STEP award. 
GC acknowledges partial support from the Labex-LIO (Lyon Institute of Origins) under grant ANR-10-LABX-66 and FRAMA (FR3127, F\'ed\'eration de Recherche ``Andr\'e Marie Amp\`ere").
IPI acknowledges funding from \textit{Fun\-da\-\c{c}\~{a}o para a Ci\^{e}ncia e a Tecnologia} (FCT)
through the Investigator contract IF/00989/2014/CP1214/CT0004
under the IF2014 Program and through FCT contracts UID/FIS/00777/2013 and CERN/FIS-NUC/0010/2015,
which are partially funded through POCTI, COMPETE, QREN, and the European Union. 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bib}
%\bibliographystyle{unsrt}
%\bibliographystyle{jhep}
\bibliographystyle{JHEP-2}

\end{document}


